Universal Anonymous Signatures

### 2022-05-12 prism-backend/research/gsac/preliminaries.tex
Working on intro.
Intro and conclusions done. Revised abstract.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

{Preliminaries}
\label{sec:preliminaries}

\subsection{Related Work}
\label{ssec:related}

@@

% One difference between our current approach to GSAC, and the existing ABGS
% works, is that in ABGS each group member can only get one credential. On the
% other hand, we are trying to let any group member obtain as many credentials
% as he wishes, possibly with different attributes, albeit all of them related to
% the same user key pair (if a different user key pair is employed, then this is
% considered as a different user).

@@

\paragraph{Digital Signatures.} %
Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
verification key \Svk. We rely on existentially unforgeable digital signature
schemes.

\paragraph{Public-Key Encryption.} %
Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
public-key encryption schemes.

\paragraph{(Vector) Commitment Schemes.} %
Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
\gets \CCommit(\Cparm, \smsg; r)$ produces a commitment \Ccom over a set of
messages \smsg, using randomness $r$ (which we may omit when explicitly
stating it is not necessary). We will further use commitment schemes that
allow committing to vectors of messages. Therein, the \CCommit algorithm simply
receives a vector of messages. In both cases, we require hiding and binding
(vector) commitment schemes.

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, or commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
For this purpose, we define such schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,
\SBCMCom,\SBCMSign,\SBCMVerify)$. Algorithm $\SBCMparm \gets
\SBCMSetup(\SBCMsecpar)$ produces the public parameters for the scheme.
$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a verification-signing
key pair. $\SBCMsig/\bot \gets\langle \SBCMCom(\SBCMvk,\overline{smsg},\smsg),
\SBCMSign(\SBCMsk,\smsg) \rangle$ is an interactive protocol between a user, who
runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
and a signer, who owns signing key \SBCMsk; both also receive common input a
block of messages \smsg. The output of the protocol is a signature over
$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\SBCMvk,
\SBCMsig,\widetilde{\smsg})$ verifies a signature \SBCMsig over message set
$\widetilde{\smsg}$, which must contain both the messages that were signed as
a block commitment as well as those signed in ``the clear''. In addition, the
produced signatures must be compatible with (efficient) NIZK proofs of knowledge
of a signature, and of (arbitrary) claims over the signed (committed) messages.
An \SBCM scheme must provide \todo{one-more-forgery} type of security.

\paragraph{Non-Interactive Zero-Knowledge.} %
We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
model. Informally, a NIZK scheme over an NP relation \NIZKRel is defined as a
tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,\NIZKVerify^\NIZKRel)$.
Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel(\NIZKsecpar)$ produces the common
reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProve^\NIZKRel(\NIZKcrs,
\NIZKx,\NIZKw)$ creates a NIZK proof of knowledge of witness \NIZKw for \NIZKx
such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerify^\NIZKRel
(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
further need schemes that provide simulation-extractability, which in a nutshell
means that no adversary can produce a proof from which we cannot extract a
witness, even after seeing polynomially many simulated proofs. To model
simulation-extractable NIZKs, we further need algorithms \NIZKSimSetup,
\NIZKSim, and \NIZKExtract, that allow simulating proofs and extracting
witnesses. The properties we build on are completeness, soundness,
zero-knowledgeness, and simulation-extractability.

@@

\todo{Attribute space. Used in generic construction of GSAC for now. Define it
  to be the set of bitstrings of some length.}

\todo{\attrs and \dattrs (in \secref{ssec:construction-gsac}, they are treated
  as indices, but I think that's not the case elsewhere).}

\todo{In \secref{ssec:construction-gsac}, we assume that all messages and
  attributes can be encoded as elements in $\ZZ^*_p$.}

\todo{In \secref{ssec:generic-construction-uas} we use $\usk \in \cred$ to
  denote the claim ``\usk is an attribute attested in \cred''.}

\todo{In GSAC traceability proof, we use $\negl(\cdot)$ to denote negligible
  functions.}

>>>>

\section{Preliminaries}
\label{sec:preliminaries}

\iffalse
\subsection{Related Work}
\label{ssec:related}

@@

% One difference between our current approach to GSAC, and the existing ABGS
% works, is that in ABGS each group member can only get one credential. On the
% other hand, we are trying to let any group member obtain as many credentials
% as he wishes, possibly with different attributes, albeit all of them related to
% the same user key pair (if a different user key pair is employed, then this is
% considered as a different user).
\fi

@@

\paragraph{Digital Signatures.} %
Defined as a tuple (\SSetup,\SKeyGen,\SSign,\SVerify). Algorithm $\parm \gets
\SSetup(\secpar)$ produces public parameters for the other algorithms.
$(\vk,\sk) \gets \SKeyGen(\parm)$ generates the verification-signing key
pair, algorithm $\sig \gets \SSign(\sk,\msg)$ signs message \msg with
signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\vk,
\sig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
verification key \Svk. We rely on existentially unforgeable digital signature
schemes.

\paragraph{Public-Key Encryption.} %
Defined as a tuple (\ESetup,\EKeyGen,\EEnc,\EDec). Algorithm $\parm \gets
\ESetup(\secpar)$ produces public parameters for the other algorithms.
$(\ek,\dk) \gets \EKeyGen(\parm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\ek,\msg)$ encrypts message \msg with
encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
public-key encryption schemes.

\paragraph{(Block) Commitment Schemes.} %
Defined as a tuple (\CSetup,\CCommit). Algorithm $\parm \gets
\CSetup(\secpar)$ produces the parameters for committing to values. $\Ccom
\gets \CCommit(\parm, \smsg; r)$ produces a commitment \Ccom over a set of
messages \smsg, using randomness $r$ (which we may omit when explicitly
stating it is not necessary). We will further use commitment schemes that
allow committing to vectors of messages. Therein, the \CCommit algorithm simply
receives a block of messages. In both cases, we require hiding and binding
(block) commitment schemes.

\paragraph{Non-Interactive Zero-Knowledge.} %
We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
model. Informally, a NIZK scheme over an NP relation \NIZKRel is defined as a
tuple ($\NIZKSetupRel$,$\NIZKProveRel$,$\NIZKVerify^\NIZKRel$).
Algorithm $\NIZKcrs \gets \NIZKSetupRel(\NIZKsecpar)$ produces the common
reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProveRel(\NIZKcrs,
\NIZKx,\NIZKw)$ creates a NIZK proof of knowledge of witness \NIZKw for \NIZKx
such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerifyRel
(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
further need schemes that provide simulation-extractability, which in a nutshell
means that no adversary can produce a proof from which we cannot extract a
witness, even after seeing polynomially many simulated proofs. To model
simulation-extractable NIZKs, we further need algorithms \NIZKSimSetup,
\NIZKSim, and \NIZKExtract, that allow simulating proofs and extracting
witnesses. The properties we build on are completeness, soundness,
zero-knowledgeness, and simulation-extractability.

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, or commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
\SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
produces the public parameters for the scheme.
$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
key pair. $\\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
  \SBCMSign(\sk,\smsg) \rangle$ is an interactive protocol between a user, who
runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
and a signer, who owns signing key \SBCMsk; both also receive common input a
block of messages \smsg. The output of the protocol is a signature over
$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
\sig,\overline{\smsg},\smsg)$ verifies a signature \SBCMsig over message set
$\overline{\smsg} \cup \smsg$. In addition, the
produced signatures must be compatible with (efficient) NIZK proofs of knowledge
of a signature, and of (arbitrary) claims over the signed (committed) messages.
An \SBCM scheme must provide one-more-forgery type of security.

@@

We use common notation habits. $y \gets A(x)$ means that algorithm $A$, on input
$x$, produces output $y$. When $A$ is a probabilistic process, and we want to
make explicit the randomness $r$, we use $y \gets A(x;r)$. $\langle y_A,y_B \gets
\langle A(x_A),B(x_B)\rangle$ denotes algorithms $A$ and $B$, running an
interactive protocol, where $A$ receives $x_A$ as input and produces $y_A$ as
output, and $B$ receives $x_B$ and produces $y_B$.
%
Our generic constructions
rely on the previously defined building blocks, which share common (but different
tokens): e.g., we will resort to several NIZK proofs instances. To distinguish
them, we may use subscripts or superscripts: e.g., $\NIZKRel_A$ denotes the
NP relation used within some algorithm $A$, $\NIZKSetupRel$ means that
the setup algorithm of an underlying NIZK system is performed associated to
relation $\NIZKRel$; $\SBCMparm$ are the public parameters for an \SBCM scheme,
and $\Eparm$ are the public parameters for an encryption scheme. Variables
written in bold font denote sets, e.g., while we use \ipk to denote a single
issuer public key, \sipk denotes a set of issuer's public keys.
%
We also assume the existence of a well defined attribute space over which
issuers in our schemes can issue credentials on. We denote this set with
\AttrSpace.

% \todo{Attribute space. Used in generic construction of GSAC for now. Define it
%   to be the set of bitstrings of some length.}

% \todo{\attrs and \dattrs (in \secref{ssec:construction-gsac}, they are treated
%   as indices, but I think that's not the case elsewhere).}

% \todo{In \secref{ssec:construction-gsac}, we assume that all messages and
%   attributes can be encoded as elements in $\ZZ^*_p$.}

% \todo{In \secref{ssec:generic-construction-uas} we use $\usk \in \cred$ to
%   denote the claim ``\usk is an attribute attested in \cred''.}

% \todo{In GSAC traceability proof, we use $\negl(\cdot)$ to denote negligible
%   functions.}

### 2022-05-12 prism-backend/research/gsac/sec-uas.tex
Added high-level descriptions of how to build other schemes from UAS.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

Furthermore, to make the concept more flexible, we no longer restrict to the
case of one issuer and one opener. Instead, \UAS supports multiple issuers (as
in generalized variants of anonymous credentials), as well as multiple openers,
each one with a predefined inspection function. Thus, it supports use cases like
having a user produce a signature with credentials obtained from issuers A and
B, which can be inspected by opener C; but later use the same credentials
from issuers A and B, to produce a signature that can be inspected by opener D.
A consequence of this is that the concept of ``group'', which was very present
in \GSAC, is now blurred in \UAS, and we get closer to the context of anonymous
credentials -- while still offering the accountability we inherit from \GSAC
via \Open and \Judge.

\input{model-uas.tex}
\input{construction-uas.tex}
\input{security-uas.tex}

>>>>

Furthermore, to make the concept more flexible, we no longer restrict to the
case of one issuer and one opener. Instead, \UAS supports multiple issuers (as
in generalized variants of anonymous credentials), as well as multiple openers,
each one with a predefined open function. Thus, it supports use cases like
having a user produce a signature with credentials obtained from issuers A and
B, which can be inspected by opener C; but later use the same credentials
from issuers A and B, to produce a signature that can be inspected by opener D.
A consequence of this is that the concept of ``group'', which was very present
in \GSAC, is now blurred in \UAS, and we get closer to the context of anonymous
credentials -- while still offering the accountability we inherit from \GSAC
via \Open and \Judge.

\input{model-uas.tex}
\input{construction-uas.tex}
\input{security-uas.tex}
\input{transformations-uas.tex}

### 2022-05-12 prism-backend/research/gsac/security-gsac.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

\begin{theorem}[Correctness of \GSACGen]
  \label{thm:correctness-gsac}
  If the underlying schemes for \todo{xxx}, our generic construction \GSACGen
  satisfies correctness as defined in \defref{def:correctness-gsac}.
\end{theorem}

@@

\begin{theorem}[Non-frameability of \GSACGen]
  \label{thm:frame-gsac}
  If the scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme for
  $\NIZK^{\Sign}$ is zero-knowledge and sound, the scheme for $\NIZK^{\Open}$ is
  sound, and the commitment scheme \C is hiding, then our generic \GSACGen
  construction satisfies non-frameability as defined in \defref{def:frame-gsac},
  except with negligible probability.
\end{theorem}

>>>>

\begin{theorem}[Correctness of \GSACGen]
  \label{thm:correctness-gsac}
  If the underlying \SBCM, encryption, and commitment schemes are correct, and
  the NIZK systems for $NIZKRel_{\Issue}$, $NIZKRel_{\Sign}$, and $NIZKRel_{\Open}$
  are also correct, our generic construction \GSACGen
  satisfies correctness as defined in \defref{def:correctness-gsac}.
\end{theorem}

@@

\begin{theorem}[Non-frameability of \GSACGen]
  \label{thm:frame-gsac}
  If the NIZK schemes for $\NIZKRel_{\Issue}$ is zero-knowledge, the scheme for
  $\NIZKRel_{\Sign}$ is zero-knowledge and sound, the scheme for $\NIZKRel_{\Open}$ is
  sound, and the commitment scheme \C is hiding, then our generic \GSACGen
  construction satisfies non-frameability as defined in \defref{def:frame-gsac},
  except with negligible probability.
\end{theorem}

### 2022-05-12 prism-backend/research/gsac/security-uas.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

\begin{theorem}[Correctness of \CUASGen]
  \label{thm:correctness-uas}
  If the underlying schemes for vector commitments, encryption, digital
  signatures, signatures on blocks of committed messages, and NIZKs are
  correct, our generic construction \CUASGen satisfies correctness as
  defined in \defref{def:correctness-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
  \todo{XXX}
\end{proof}

@@

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is zero-knowledge, sound,
  and simulation extractable, the NIZK scheme for $\NIZKRel_{\Inspect}$ is sound
  and simulation extractable, and \SBCM is one-more unforgeable, then our
  \CUASGen construction satisfies signing unforgeability as defined in
  \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

@@

  Cases 1, 2 and 3 above account for winning conditions at steps 6 and 10.
  % 
  Additionally, $\adv$ wins at step 8 if $\feval(\usk,\scred,\msg) \neq \yeval$,
  where \yeval is the value output by the adversary in step 2. However, since
  $\Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$, soundness of $NIZK^{\Sign}$
  implies that this has negligible probability.
  %
  Similarly, $\adv$ wins at step 9 if (1) $\finsp(\yeval,\usk,\scred,\msg) \neq
  \yinsp$, where \yinsp is the value output by \Inspect at line 5; or if (2)
  $\yinsp \neq \yinsp'$, where $\yinsp'$ is the value extracted by \ExtractSign
  at step 7. For (1), soundness of $\NIZK^{\Sign}$ ensures that \yinsp is the
  correct evaluation of \finsp, whereas soundness of $\NIZK^{\Inspect}$ and
  correctness of the public key encryption ensure that this is also the value
  output by \Inspect. Thus, the probability of $\adv$ winning the game because
  of (1) is negligible. Finally, for (2), simulation-extractability of
  $\NIZK^{\Inspect}$ and correctness of the public key encryption ensure that
  the $\yinsp'$ value extracted by \NIZKExtract matches the value produced by
  \Inspect.

@@

  For $G_1$, within \Setup, we replace the \Setup algorithms for the three
  NIZKs (\Issue, \Sign and \Inspect) with their corresponding \SimSetup
  variants. Consequently, the corresponding queries to \Prove are also
  simulated via the simulator. By the zero-knowledge property of the NIZK
  systems, $G_1$ is indistinguishable from $G_0$.

>>>>

\begin{theorem}[Correctness of \CUASGen]
  \label{thm:correctness-uas}
  If the underlying schemes for commitments, encryption and \SBCM, are correct,
  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
  defined in \defref{def:correctness-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
  Moreover, all the credentials employed to honestly produce the signature,
  identified with \scid, meet their respective issuance policies due to
  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
  output of \feval matches \yeval at line $10$, which is furthermore computed
  over $\usk=\UK[\uid]$ due to correctness of the commitment scheme. Finally,
  correctness of the NIZKs for $\NIZKRel_{\Sign}$ and $\NIZKRel_{\Open}$, and
  correctness of the encryption scheme, ensure that \Judge accepts the proof
  produced by \Open, and \yinsp is the correct value for the chosen
  $\finsp^{\oid}$.
\end{proof}

@@

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is zero-knowledge, sound,
  and simulation extractable, the NIZK scheme for $\NIZKRel_{\Open}$ is sound
  and simulation extractable, and \SBCM is one-more unforgeable, then our
  \CUASGen construction satisfies signing unforgeability as defined in
  \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

@@

  Cases 1, 2 and 3 above account for winning conditions at steps 6 and 10.
  % 
  Additionally, $\adv$ wins at step 8 if $\feval(\usk,\scred,\msg) \neq \yeval$,
  where \yeval is the value output by the adversary in step 2. However, since
  $\Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$, soundness of $NIZK^{\Sign}$
  implies that this has negligible probability.
  %
  Similarly, $\adv$ wins at step 9 if (1) $\finsp(\yeval,\usk,\scred,\msg) \neq
  \yinsp$, where \yinsp is the value output by \Open at line 5; or if (2)
  $\yinsp \neq \yinsp'$, where $\yinsp'$ is the value extracted by \ExtractSign
  at step 7. For (1), soundness of $\NIZK^{\Sign}$ ensures that \yinsp is the
  correct evaluation of \finsp, whereas soundness of $\NIZK^{\Open}$ and
  correctness of the public key encryption ensure that this is also the value
  output by \Open. Thus, the probability of $\adv$ winning the game because
  of (1) is negligible. Finally, for (2), simulation-extractability of
  $\NIZK^{\Open}$ and correctness of the public key encryption ensure that
  the $\yinsp'$ value extracted by \NIZKExtract matches the value produced by
  \Open.

@@

  For $G_1$, within \Setup, we replace the \Setup algorithms for the three
  NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
  variants. Consequently, the corresponding queries to \Prove are also
  simulated via the simulator. By the zero-knowledge property of the NIZK
  systems, $G_1$ is indistinguishable from $G_0$.

### 2022-05-12 prism-backend/research/gsac/transformations-uas.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

\section{Relating \UAS with Other Schemes, and Variations}
\label{ssec:transformations}

In order to justify \UAS's universality, in this section we describe how does
\UAS schemes relate with other similar systems. \todo{The relationships seem
  quite straightforward; thus, we only informally sketch how one could build
  other schemes (or something very similar to them) from \UAS, and leave the
  formal analysis for futher work.}
%
As a first (informal) observation, we note that the same transformation to
interactive presentations as described in \GSAC applies here.

@@

\todo{In \cite{khk+19}, the authors prove that GS-MDO implies identity-based
  encryption. \UAS implying GS-MDO would thus imply IBE, but we do not use
  IBE in our constructions. Is there some connection between some of the main
  building blocks we use, and IBE?}

@@

In a nutshell, ring signatures \needcite are like group signatures where
rather than having an issuer accepting users into a group, any user can create
an ad hoc group composed by himself, and any arbitrary set of other users that
have advertised their public keys in some publicly accessible way. Also, in
ring signatures no de-anonymization is possible\footnote{At least, in vanilla
  ring signatures. Some variants allow some sort of linkability; for instance
  \needcite}, although the most distinguishing property is probably the lack of
issuer, which has led some relevant systems like Monero%
\footnote{\url{https://www.getmonero.org/resources/moneropedia/ringsignatures.html}.
  Last access on May 8th, 2022.} to opt for ring signatures rather than, e.g.,
group signatures.

@@

With this alternative definition, we can achieve a generalisation of MPS
basically by, insted of returning the plaintext \yeval value, returning an
encryption of it under the inspector's public key; additionally proving 
that the value used to compute the output of \finsp is the plaintext \yeval
value. In more detail, given any \feval function, we first define an
encrypted variant $\feval^{enc}(\usk,\scred,\msg) \coloneqq \lbrace \yeval
\gets \feval(\usk,\scred,\msg); \yeval' \gets \EEnc(\opk,\yeval); \pcreturn
\yeval' \rbrace$.
%
Naturally, the $\NIZKRel_{\Sign}$ has to be correspondigly extended, as
$\NIZKRel_{\Sign}^{enc} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,
\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \EEnc(\opk,\feval(\usk,\scred,\msg)) \land \yinsp = \finsp(\feval(\usk,
\scred,\msg),\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$.

@@

\todo{It would seem that the simulation-based anonymity definition is more
  general. Can we prove that? Concretely, if it is also good for selective
  disclosure, we may just adopt it as default.}

@@

\subsection{Functional Signatures}

\todo{I think that, by making \yeval explicit, \UAS is essentially a
  privacy-preserving extension to Functional Signatures. Still, I read that paper
  quite some time ago. Re-check.}

>>>>

\section{Relating \UAS with Other Schemes, and Variations}
\label{sec:transformations}

In order to justify \UAS's universality, in this section we describe how does
\UAS schemes relate with other similar systems. \jdv{The relationships seem
  quite straightforward; thus, we only informally sketch how one could build
  other schemes (or something very similar to them) from \UAS, and leave the
  formal analysis for futher work.}
%
As a first (informal) observation, we note that the same transformation to
interactive presentations as described in \GSAC applies here.

@@

\jdv{In \cite{khk+19}, the authors prove that GS-MDO implies identity-based
  encryption. \UAS implying GS-MDO would thus imply IBE, but we do not use
  IBE in our constructions. Is there some connection between some of the main
  building blocks we use, and IBE?}

@@

In a nutshell, ring signatures \cite{rst06} are like group signatures where
rather than having an issuer accepting users into a group, any user can create
an ad hoc group composed by himself, and any arbitrary set of other users that
have advertised their public keys in some publicly accessible way. Also, in
ring signatures no de-anonymization is possible\footnote{At least, in vanilla
  ring signatures. Some variants allow some sort of linkability; for instance
  \cite{lww04}}, although the most distinguishing property is probably the lack
of issuer, which has led some relevant systems like Monero%
\footnote{\url{https://www.getmonero.org/resources/moneropedia/ringsignatures.html}.
  Last access on May 8th, 2022.} to opt for ring signatures rather than, e.g.,
group signatures.

@@

With this alternative definition, we can achieve a generalisation of MPS
basically by, insted of returning the plaintext \yeval value, returning an
encryption of it under the opener's public key; additionally proving 
that the value used to compute the output of \finsp is the plaintext \yeval
value. In more detail, given any \feval function, we first define an
encrypted variant $\feval^{enc}(\usk,\scred,\msg) \coloneqq \lbrace \yeval
\gets \feval(\usk,\scred,\msg); \yeval' \gets \EEnc(\opk,\yeval); \pcreturn
\yeval' \rbrace$.
%
Naturally, the $\NIZKRel_{\Sign}$ has to be correspondigly extended, as
$\NIZKRel_{\Sign}^{enc} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,
\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \EEnc(\opk,\feval(\usk,\scred,\msg)) \land \yinsp = \finsp(\feval(\usk,
\scred,\msg),\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$.

@@

\jdv{It would seem that the simulation-based anonymity definition is more
  general. Can we prove that? Concretely, if it is also good for selective
  disclosure, we may just adopt it as default.}

@@

\jdv{\subsection{Functional Signatures}}
\jdv{I think that, by making \yeval explicit, \UAS is essentially a
  privacy-preserving extension to Functional Signatures. Still, I read that paper
  quite some time ago. Re-check.}
